---
title: "R for finance Project 02"
author: "Zarif"
date: "`r Sys.Date()`"
output:
 html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: true
    number_sections: true
    css: mystyle.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

# Portfolio analysis 

R script seems to be designed for conducting a financial analysis of a portfolio consisting of several assets. Here's a breakdown of the different sections of your script and what they contribute to the analysis: 


# Nessary steps:

-   **Setup and Libraries:** We begin by loading necessary libraries such as dplyr, quantmod, and PerformanceAnalytics for data manipulation and financial analysis.



```{r, echo=FALSE}
library(dplyr)
library(quantmod)
library(PerformanceAnalytics)
```

-   **Data Retrieval:** We define the tickers for the assets of The Procter & Gamble Company (PG), Verizon Communications Inc. (VZ), The Coca-Cola Company (KO), and General Electric Company (GE) form NYSE. Using a loop, that we retrieve historical price data for each asset from Yahoo Finance and store it in a dataframe portfolioPrices.

```{r}
tickers <- c("PG", "VZ", "KO", "GE")
weights <- c(.30, .25, .25, .20)
```



```{r, echo=FALSE}
#Geting Prices
portfolioPrices <- NULL

for (i in tickers){
  portfolioPrices <- cbind(portfolioPrices,
                           getSymbols.yahoo(i, from="2012-01-01", periodicity = "daily",auto.assign=FALSE)[,6])
}
```


-   **Benchmark Data:** We retrieve benchmark data (in this case, represented by the ETF "IWM") to compare the portfolio performance against, and calculate returns from the benchmark data and handle missing values.

```{r}
# bench mark
benchmarkPrices <- getSymbols.yahoo("IWM", from="2012-01-01", periodicity = "daily", auto.assign=FALSE)[,6]

colSums(is.na(benchmarkPrices)) # is there any NA value

benchmarkReturns <- na.omit(ROC(benchmarkPrices, type="discrete"))
```
-   **Data Preprocessing:** Then rename the columns of portfolioPrices dataframe with ticker symbols. Check for missing values in the portfolio price data.

```{r}
#Rename Columns
colnames(portfolioPrices) <- tickers
#Get sum of NA per column
colSums(is.na(portfolioPrices))
```

# Visualization:

Plot the historical prices of assets in the portfolio using plot() function.

```{r, echo=FALSE}
#Plot
plot(portfolioPrices, legend = tickers, main = "Portfolio Prices")
```

# Return Calculation:

Calculate daily returns for each asset in the portfolio and handle missing values. Calculate the portfolio returns using Return.portfolio() function.

```{r}
#Calculate Returns For DF
dailyReturns <- na.omit(ROC(portfolioPrices, type="discrete"))

#Calculate Portfolio Returns
portfolioReturn <- Return.portfolio(dailyReturns, weights=weights)
```

# Performance Visualization: 

Plot the cumulative returns of the portfolio using chart.

## CumReturns

```{r, echo=FALSE}
#Plot Performance
chart.CumReturns(portfolioReturn)
```

## PerformanceSummary

```{r, echo=FALSE}
charts.PerformanceSummary(portfolioReturn)
```

## Bar

```{r, echo=FALSE}
chart.Bar(portfolioReturn)
```

## Boxplot

```{r, echo=FALSE}
chart.Boxplot(portfolioReturn)
```

## RollingPerformance

```{r, echo=FALSE}
charts.RollingPerformance(portfolioReturn)
```

# Risk Metrics:

Calculate CAPM beta of the portfolio against the benchmark, both in general and during bullish and bearish market conditions.

## Beta

```{r, echo=FALSE}
#Calculate Metrics 
CAPM.beta(portfolioReturn, benchmarkReturns, .025/252)
```

## Beta.bull

```{r, echo=FALSE}
CAPM.beta.bull(portfolioReturn, benchmarkReturns, .025/252)
```

## Beta.bear

```{r, echo=FALSE}
CAPM.beta.bear(portfolioReturn, benchmarkReturns, .025/252)
```

## Jensen Alpha

Calculate CAPM Jensen's alpha to measure the portfolio's risk-adjusted returns.
Compute the Sharpe Ratio to assess the portfolio's risk-adjusted returns relative to the risk-free rate.

```{r, echo=FALSE}
CAPM.jensenAlpha(portfolioReturn, benchmarkReturns, .025/252)
```

# Performance Metrics:

Generating a table of annualized returns adjusted for risk-free rate. Provide a table of calendar returns.

```{r, echo=FALSE}
SharpeRatio(portfolioReturn, Rf = .025/252, p = 0.95, FUN = "StdDev",
            weights = NULL, annualize = FALSE)
```

Finally, it involve interpreting the visualizations, risk metrics, and performance metrics to draw conclusions about the portfolio's performance and risk characteristics.

```{r, echo=FALSE}
table.AnnualizedReturns(portfolioReturn, Rf=.025/252, geometric=TRUE)
```



```{r, echo=FALSE}
table.CalendarReturns(portfolioReturn)
```

