---
title: "R Program Visualization Project"
author: "Md. Zarif Ibtehaj Emon"
date: "2023-10-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

# Scatterplot

## MTCARS Data

We can see the differences between the Horsepower vs. MPG from mtcars. We found out that the MPG and Horsepower of most cyl is 8 which is more than other cyl.

```{r}
library(tidyverse)
library(ggplot2)

#data from mtcars
data("mtcars")

# Create the Scatterplot
mtcars_plot <- ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point(aes(color = as.factor(cyl)), shape = "diamond", size = 4) +
  geom_line(color = "firebrick", linetype = "dotted", lwd = 0.3) +
  geom_smooth(method = "lm", col = "#EE2C2C", size = 1) + 
  
  labs(title = "Horsepower vs. MPG for mtcars",
       x = "Horsepower",
       y = "MPG",
       caption = "Linear Regression Line") +
  
  theme_test()

# Set legend labels
mtcars_plot <- mtcars_plot + scale_color_discrete(name = "cyl")

# Display the plot
mtcars_plot
```

# Barplot

## Data from WHO Corona virus (COVID-19) Dashboard

In Bangladesh, many people have been killed by the COVID-19 pandemic. Data from the WHO Corona virus (COVID-19) Dashboard is available from 2020 to 2023. (last updates)

```{r}
library(ggplot2)

# Data from WHO Corona virus (COVID-19) Dashboard
data <- data.frame(
  Year = factor(c(2020, 2021, 2022, 2023)),  # Convert Year to a factor
  Deaths = c(7559, 20513, 1368, 37))

# Custom colors for the bars
bar_colors <- c("#EEB4B4", "#7FCAE6", "#B6D7A8", "#FFD700")

# Creating the Barplot
die <- ggplot(data, aes(x = Year, y = Deaths, fill = Year)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Deaths), vjust = -0.5, size = 4, color = "black") +
  
  labs(title = "COVID-19 Deaths",
    subtitle = "Bangladesh (2020-2023)",
    x = "Year",
    y = "Number of Deaths" ) +
  
  scale_fill_manual(values = bar_colors) +  # Setting custom colors
  
  theme_classic()

# Display the plot
die
```

# Animation

## Annual Death in Bangladesh

Using Data from "macrotrends" to calculate the annual death rate in Bangladesh. You can download the CSV file to see Bangladesh's history and forecasted assumption of death.

You can find in this link: (<https://www.macrotrends.net/countries/BGD/bangladesh/death-rate>)

```{r}
library(gganimate)

# Load data from the CSV file
data <- read.csv("~/Rstudio/Bangladesh_Death_Rate.csv")

# Create the animated point
ad <- ggplot(data, aes(x = Year, y = Deaths_per_1000_People)) +
  geom_point(color = "#F0FFFF", size = 3, alpha = 0.7) + 
   
  labs(title = "Annual Deaths",
    subtitle = "Deaths per 1000 People",
    x = "Year",
    y = "Number of Deaths Rate") +
  
    transition_states(Year, transition_length = 2, state_length = 1) +
    shadow_wake(.3) +
    ease_aes('linear') +
    
    theme_minimal()+
    
    theme(panel.background = element_rect(fill = "#4d4d4d")) #changing Bacground color
  
# Animate the plot
anim <- animate(ad, nframes = 75)

# Display the animation
anim

#save animation
anim_save("Annual_Deaths.gif", anim)
```
